Time Series Bootstrapping For Solar Current

### 2021-12-06 deliverables/presentation.Rmd
Slight rearrangement, dropped trailing whitespace

---
title: "Time Series Bootstrapping For Solar Current"
author: "Evan Kessler, Adam Kiehl, and Boston Lee"
date: "2021/12/9"
output: 
  beamer_presentation: default
---

@@

@@

- National Solar Radiation Database (NSRD) from National Renewable Energy Laboratory (NREL) accessed through API
- Los Angeles data (1998-2010) was used to replicate the source paper. (IS THE YEAR RANGE RIGHT BOSTON?)
    - Date and time, direct normal irradiance (DNI), and temperature data used.

>>>>

---
title: "Time Series Bootstrapping For Solar Current"
author: "Evan Kessler, Adam Kiehl, and Boston Lee"
date: "2021/12/9"
output:
  beamer_presentation: default
bibliography: references.bib
---

@@

# Motivation

@@

- National Solar Radiation Database (NSRD) from National Renewable Energy Laboratory (NREL) accessed through API
- Los Angeles data (1998-2010) was used to replicate the source paper.
    - Date and time, direct normal irradiance (DNI), and temperature data used.
